Cycle Route Uptake and Scenario Estimation (CRUSE): an approach for developing strategic cycle network planning tools

### 2024-06-26 paper.qmd
Fix fig 6 size
Re-word description of Parkin work

Area-based approaches were developed before network-based tools, such as a 2007 regression-based model to estimate the percentage of cycling trips to work in England and Wales based on socioeconomic, transportation, and physical factors at the small area (wards) level in 2007 [@parkin_estimation_2007].
They found that areas with a higher percentage of females, non-whites, car ownership, lower socioeconomic classes, income, distance to work, population density, poor highway conditions, hills, rainfall, and fewer off-road bicycle routes tended to have a lower proportion of cycling to work.
The approach also generated "forecasts for potential levels of bicycle use" with increases in off-road routes, improvements of highway and, conversely, increases in car ownership and distance to work leading to decreases in cycling to work.

@@

::: {#fig-city-results}
![](rnet_types.png)

>>>>

Area-based approaches were developed before network-based tools, such as a 2007 regression-based model to estimate the percentage of cycling trips to work in England and Wales based on socioeconomic, transportation, and physical factors at the small area (wards) level in 2007 [@parkin_estimation_2007].
They found that areas with a higher percentage of females, non-whites, car ownership, lower socioeconomic classes, income, distance to work, population density, poor highway conditions, hills, rainfall, and fewer off-road bicycle routes tended to have a lower proportion of cycling to work.
The approach also generated "forecasts for potential levels of bicycle use" associated with increasing in off-road routes and, conversely, increasing car ownership levels and distances travelled to work leading to decreases in cycling.

@@

::: {#fig-city-results}

![](rnet_types.png){width="90%"}
